\subsubsection*{Previous papers}

Regarding the main focus point of this assignment there are plenty of papers comparing the performance of different threading programming
models. Scott R. Taylor et al. \cite{multithreading-comparison} compared the performance of cilk, pthreads and Java threads. Their approach
was to parallelize the fibonacci algorithm and to compare the performance of the different threading models. Their methodology was a time
comparison between the three different models. They found that the cilk model was the fastest one and the Java threads model was the slowest one.

On a more comprehensive level, Ensar Ajkunic et al. \cite{5-parallel-models} compared the performance of five different parallel programming models.
Pthread, OpenMP, Threading Building Blocks, Cilk++ and MPI. Their approach was similar to the one of Taylor et al. \cite{multithreading-comparison}
They compared the execution time of the algorithm written in the 5 models. The key difference was that they used matrix multiplication as the 
benchmarking algorithm. Their results also included speed up trends compared to the sequential implementation. 

At last but not least Solmaz Salehian et al. \cite{threading-models} compared the performance of multiple threading models using multiple algorithms.
The methodology was slightly different from the previous two papers. Along with the execution time they also compared the ability of the models to
scale on multiple cores and the performance gains from using more physical cores.